Baseline centering problem

### 2019-01-14 paper/tangotd.tex

By multiplying \eqref{eq:optrightbellman} by $V$, one finds the
Newton--Bellman equation for the optimal function $V$ seen as a matrix:
\begin{equation}
\label{eq:optrightbellman}
V^2_{s_1s_2}=V_{s_1s_2}+\gamma \sum_{s_3} V_{s_1s_3}\max_a
\E_{s_4|s_3,a} V_{s_4s_2}
\end{equation}
TODO DOUBLE-CHECK
and representing $V$ by its density wrt $\rho$ namely
$V_{s_1s_2}=z(s_1,s_2)\rho(s_2)$ this suggests the Newton method
\begin{equation}
z(s_1,s_2)\gets 2z(s_1,s_2)-\E_{s_3\sim \rho} z(s_1,s_3)z(s_3,s_2)+\gamma
\E_{s_3\sim \rho} z(s_1,s_3)\max_a \E_{s_4\sim P(s_4|s_3,a)} z(s_4,s_2)
\end{equation}
satisfied by the optimal $z$ function.

>>>>

By multiplying \eqref{eq:optrightbellman} by $V$, one finds the
Newton--Bellman equation for the optimal function $V$ seen as a matrix:
\begin{equation}
\label{eq:optrightbellman}
V^2_{s_1s_2}=V_{s_1s_2}+\gamma \sum_{s_3} V_{s_1s_3}\max_a
\E_{s_4|s_3,a} V_{s_4s_2}
\end{equation}
TODO CHECK, MAY BE WRONG DUE TO MAX OF WRONG STUFF!!
and representing $V$ by its density wrt $\rho$ namely
$V_{s_1s_2}=z(s_1,s_2)\rho(s_2)$ this suggests the Newton method
\begin{equation}
z(s_1,s_2)\gets 2z(s_1,s_2)-\E_{s_3\sim \rho} z(s_1,s_3)z(s_3,s_2)+\gamma
\E_{s_3\sim \rho} z(s_1,s_3)\max_a \E_{s_4\sim P(s_4|s_3,a)} z(s_4,s_2)
\end{equation}
satisfied by the optimal $z$ function.
